Supporting Information

### 2018-03-23 SupportingInformation.Rmd
minor correction

Table \ref{tab_count_bestcop} shows that several copulas are much better supported than the Gaussian copula, answering the first part of question 1 for these data. Table \ref{tab_count_AICw} represents the Akaike weights of the best-fit copula for each location pair. Our fitting results are supported by the lowest-AIC copula *p*-value in the Cramer-von Mises-based test [Table \ref{tab_count_p_CvM}] of the goodness of its fit, and in the Kolmogorov-Smirnov-based test [Table \ref{tab_count_p_KS}] of the goodness of fit with atleast
`r min((RES_aphid_count$gfc_numBS_success/RES_aphid_count$gfc_numBS),na.rm=T)*100` % successful bootstrap. Table \ref{tab_count_AICw_normal} represents the Akaike weights of the normal copula for each location pair and by comparing with Table \ref{tab_count_AICw}, one can verify that for most of the locations a normal copula is not a good fit based on minimum AIC. The model-averaged (using AIC) lower-tail dependence statistic and the model-averaged (again, AIC based) upper-tail dependence statistic are presented in Table \ref{tab_count_LTdep_AICw} and Table \ref{tab_count_UTdep_AICw} respectively, and these values are distinct from what a Gaussian copula would give (i.e., 0), answering the second part of question 1 for these data. Furthermore, the difference of these two quantities (lower minus upper) in Table \ref{tab_count_LTmUT} indicates it is different from $0$ for most of the locations, answering the third part of question 1. These results do convincingly show non-Gaussian copula structure, having **`r sum((RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw)>0,na.rm=T)`** out of **`r (dim(RES_aphid_count$gfc_p_CvM)[1]^2-dim(RES_aphid_count$gfc_p_CvM)[1])-RES_aphid_count$num_indep_loc_pair`** location pair with greater lower tail dependence.

@@

Table \ref{tab_ff_bestcop} shows that several copulas are much better supported than the Gaussian copula, answering the first part of question 1 for these data. Table \ref{tab_ff_AICw} represents the Akaike weights of the best-fit copula for each location pair. Our fitting results are supported by the lowest-AIC copula *p*-value in the Cramer-von Mises-based test [Table \ref{tab_ff_p_CvM}] of the goodness of its fit, and in the Kolmogorov-Smirnov-based test [Table \ref{tab_ff_p_KS}] of the goodness of fit with atleast
`r min((RES_aphid_ff$gfc_numBS_success/RES_aphid_ff$gfc_numBS),na.rm=T)*100` % successful bootstrap. Table \ref{tab_ff_AICw_normal} represents the Akaike weights of the normal copula for each location pair and by comparing with Table \ref{tab_ff_AICw}, one can verify that for most of the locations a normal copula is not a good fit based on minimum AIC. The model-averaged (using AIC) lower-tail dependence statistic and the model-averaged (again, AIC based) upper-tail dependence statistic are presented in Table \ref{tab_ff_LTdep_AICw} and Table \ref{tab_ff_UTdep_AICw} respectively, and these values are distinct from what a Gaussian copula would give (i.e., 0), answering the second part of question 1 for these data. Furthermore, the difference of these two quantities (lower minus upper) in Table \ref{tab_ff_LTmUT} indicates it is different from $0$ for most of the locations, answering the third part of question 1. These results do convincingly show non-Gaussian copula structure, having **`r sum((RES_aphid_ff$LTdep_AICw-RES_aphid_ff$UTdep_AICw)<0,na.rm=T)`** out of **`r (dim(RES_aphid_ff$gfc_p_CvM)[1]^2-dim(RES_aphid_ff$gfc_p_CvM)[1])-RES_aphid_ff$num_indep_loc_pair`** location pair more upper tail dependence.

@@

Table \ref{tab_pns_bestcop} shows that several copulas are much better supported than the Gaussian copula, answering the first part of question 1 for these data. Table \ref{tab_pns_AICw} represents the Akaike weights of the best-fit copula for each location pair. Our fitting results are supported by the lowest-AIC copula *p*-value in the Cramer-von Mises-based test [Table \ref{tab_pns_p_CvM}] of the goodness of its fit, and in the Kolmogorov-Smirnov-based test [Table \ref{tab_pns_p_KS}] of the goodness of fit with atleast
`r min((RES_plankton_north_sea$gfc_numBS_success/RES_plankton_north_sea$gfc_numBS),na.rm=T)*100` % successful bootstrap. Table \ref{tab_pns_AICw_normal} represents the Akaike weights of the normal copula for each location pair and by comparing with Table \ref{tab_pns_AICw}, one can verify that for most of the locations a normal copula is not a good fit based on minimum AIC. The model-averaged (using AIC) lower-tail dependence statistic and the model-averaged (again, AIC based) upper-tail dependence statistic are presented in Table \ref{tab_pns_LTdep_AICw} and Table \ref{tab_pns_UTdep_AICw} respectively, and these values are distinct from what a Gaussian copula would give (i.e., 0), answering the second part of question 1 for these data. Furthermore, the difference of these two quantities (lower minus upper) in Table \ref{tab_pns_LTmUT} indicates it is different from $0$ for most of the locations, answering the third part of question 1. These results do convincingly show non-Gaussian copula structure, having `r sum((RES_plankton_north_sea$LTdep_AICw-RES_plankton_north_sea$UTdep_AICw)>0,na.rm=T)` out of `r (dim(RES_plankton_north_sea$gfc_p_CvM)[1]^2-dim(RES_plankton_north_sea$gfc_p_CvM)[1])-RES_plankton_north_sea$num_indep_loc_pair` location pair more lower tail dependence.

>>>>

Table \ref{tab_count_bestcop} shows that several copulas are much better supported than the Gaussian copula, answering the first part of question 1 for these data. Table \ref{tab_count_AICw} represents the Akaike weights of the best-fit copula for each location pair. Our fitting results are supported by the lowest-AIC copula *p*-value in the Cramer-von Mises-based test [Table \ref{tab_count_p_CvM}] of the goodness of its fit, and in the Kolmogorov-Smirnov-based test [Table \ref{tab_count_p_KS}] of the goodness of fit with atleast
`r min((RES_aphid_count$gfc_numBS_success/RES_aphid_count$gfc_numBS),na.rm=T)*100` % successful bootstrap. Table \ref{tab_count_AICw_normal} represents the Akaike weights of the normal copula for each location pair and by comparing with Table \ref{tab_count_AICw}, one can verify that for most of the locations a normal copula is not a good fit based on minimum AIC. The model-averaged (using AIC) lower-tail dependence statistic and the model-averaged (again, AIC based) upper-tail dependence statistic are presented in Table \ref{tab_count_LTdep_AICw} and Table \ref{tab_count_UTdep_AICw} respectively, and these values are distinct from what a Gaussian copula would give (i.e., 0), answering the second part of question 1 for these data. Furthermore, the difference of these two quantities (lower minus upper) in Table \ref{tab_count_LTmUT} indicates it is different from $0$ for most of the locations, answering the third part of question 1. These results do convincingly show non-Gaussian copula structure, having **`r sum((RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw)>0,na.rm=T)`** out of **`r (dim(RES_aphid_count$gfc_p_CvM)[1]^2-dim(RES_aphid_count$gfc_p_CvM)[1])-2*RES_aphid_count$num_indep_loc_pair`** location pair with greater lower tail dependence.

@@

Table \ref{tab_ff_bestcop} shows that several copulas are much better supported than the Gaussian copula, answering the first part of question 1 for these data. Table \ref{tab_ff_AICw} represents the Akaike weights of the best-fit copula for each location pair. Our fitting results are supported by the lowest-AIC copula *p*-value in the Cramer-von Mises-based test [Table \ref{tab_ff_p_CvM}] of the goodness of its fit, and in the Kolmogorov-Smirnov-based test [Table \ref{tab_ff_p_KS}] of the goodness of fit with atleast
`r min((RES_aphid_ff$gfc_numBS_success/RES_aphid_ff$gfc_numBS),na.rm=T)*100` % successful bootstrap. Table \ref{tab_ff_AICw_normal} represents the Akaike weights of the normal copula for each location pair and by comparing with Table \ref{tab_ff_AICw}, one can verify that for most of the locations a normal copula is not a good fit based on minimum AIC. The model-averaged (using AIC) lower-tail dependence statistic and the model-averaged (again, AIC based) upper-tail dependence statistic are presented in Table \ref{tab_ff_LTdep_AICw} and Table \ref{tab_ff_UTdep_AICw} respectively, and these values are distinct from what a Gaussian copula would give (i.e., 0), answering the second part of question 1 for these data. Furthermore, the difference of these two quantities (lower minus upper) in Table \ref{tab_ff_LTmUT} indicates it is different from $0$ for most of the locations, answering the third part of question 1. These results do convincingly show non-Gaussian copula structure, having **`r sum((RES_aphid_ff$LTdep_AICw-RES_aphid_ff$UTdep_AICw)<0,na.rm=T)`** out of **`r (dim(RES_aphid_ff$gfc_p_CvM)[1]^2-dim(RES_aphid_ff$gfc_p_CvM)[1])-2*RES_aphid_ff$num_indep_loc_pair`** location pair more upper tail dependence.

@@

Table \ref{tab_pns_bestcop} shows that several copulas are much better supported than the Gaussian copula, answering the first part of question 1 for these data. Table \ref{tab_pns_AICw} represents the Akaike weights of the best-fit copula for each location pair. Our fitting results are supported by the lowest-AIC copula *p*-value in the Cramer-von Mises-based test [Table \ref{tab_pns_p_CvM}] of the goodness of its fit, and in the Kolmogorov-Smirnov-based test [Table \ref{tab_pns_p_KS}] of the goodness of fit with atleast
`r min((RES_plankton_north_sea$gfc_numBS_success/RES_plankton_north_sea$gfc_numBS),na.rm=T)*100` % successful bootstrap. Table \ref{tab_pns_AICw_normal} represents the Akaike weights of the normal copula for each location pair and by comparing with Table \ref{tab_pns_AICw}, one can verify that for most of the locations a normal copula is not a good fit based on minimum AIC. The model-averaged (using AIC) lower-tail dependence statistic and the model-averaged (again, AIC based) upper-tail dependence statistic are presented in Table \ref{tab_pns_LTdep_AICw} and Table \ref{tab_pns_UTdep_AICw} respectively, and these values are distinct from what a Gaussian copula would give (i.e., 0), answering the second part of question 1 for these data. Furthermore, the difference of these two quantities (lower minus upper) in Table \ref{tab_pns_LTmUT} indicates it is different from $0$ for most of the locations, answering the third part of question 1. These results do convincingly show non-Gaussian copula structure, having **`r sum((RES_plankton_north_sea$LTdep_AICw-RES_plankton_north_sea$UTdep_AICw)>0,na.rm=T)`** out of **`r (dim(RES_plankton_north_sea$gfc_p_CvM)[1]^2-dim(RES_plankton_north_sea$gfc_p_CvM)[1])-2*RES_plankton_north_sea$num_indep_loc_pair`** location pair more lower tail dependence.
